\chapter{Introduction}

\section{Motivation: stocks control in warehouses in mall shops and in schools (space, different operators, number of operations)}

\section{Dissertation organization (to do later)}

%\section{Context}

Nespresso is owned by Nestlé Nespresso S. A., one operational 
unit of the Nestlé Group, with headquarters in Lausanne, 
Switzerland~\cite{nespressowebsite}. (...)

The proposed solution is a system around \textbf{smart shelving}. 

The structure storing the products contains RFID antennas and 
readers that detect and read the tags attach to them. Those 
readers will let the platform know in real time the state of 
the product in stock.

This system should handle the registration and verification 
of arriving stock and manage in real time warehouse products. 

The product should integrate with the logistics management 
software used by the company, allowing the a real-time 
management off all the products, machine learning predictions 
and control of the product flow.

The solution must be reliable and cheap to maintain. The 
initial investment should also be the smallest possible. 

%\section{Motivation}

With the growing of the brand, the complexity in the logistics 
networks starts to compromise the management of the products 
down in the chain. 

The categorization and verification of new inventory, inspection 
of the arrived goods from the transportation company, returns, 
control and management of stocks, are all attended by manual 
labour. 
The manual labour is prone to errors, takes a lot of working 
time and interfacing with the management software isn't usually 
efficient.

%\section{Objectives}

\begin{itemize}
  \item \textbf{Prevent stock-outs:} get timely replenishment 
  and optimizes in-store sales and management. Logistics 
  companies deliver goods on time and according to delivery 
  requirements;
  \item \textbf{Reduce time and errors from manual labour:} 
  counts, identification, misplacement and lost or stolen items;
  \item \textbf{Help customers:} find and engage with the 
  products they want;
  \item \textbf{Control:} who removes or checks out valuable 
  items;
  \item \textbf{Automatic information and management of stock:} 
  the logistics lines automatically transmits and receives 
  stock information;
  \item \textbf{Smart physical storage:} automatic 
  identification of goods in the warehouse/shelves, 
  automatic matching of distribution requirements, improves 
  the efficiency of goods storage;
  \item \textbf{Acquisition technology:} After the goods enter 
  the collection area, the collection equipment automatically 
  identifies multiple items by collecting RFID tags, thereby 
  efficiently completing the goods in and out of the warehouse, 
  ensuring whether the physical and distribution requirements 
  are consistent, and improving the efficiency of goods 
  distribution;
  \item \textbf{Real-time:} master the distribution of all 
  goods in real time, accurately grasp the inventory situation, 
  optimize the reasonable inventory, and grasp the status and 
  changes of the warehouse environment in real time;
\end{itemize}

%\cleardoublepage